---
title: "Plotly demonstration"
author: "John Lafin"
date: "11/17/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE,
                      message = FALSE)
library(tidyverse)
library(plotly)
```

## Introduction

This project draws upon the CO2 dataset. This dataset originates from an experiment on the cold tolerance of the grass species *Echinochloa crus-galli*. The plants are separated by origin (Quebec or Mississippi), and by treatment (chilled 24 h prior to measurement, or unchilled). Measurements were taken at 7 different ambient CO2 levels.

## Results

```{r}
data(CO2)
m <- CO2 %>% 
  group_by(Type, Treatment, conc) %>%
  summarize(uptake = mean(uptake))
fig <- plot_ly(data = filter(m, Treatment == 'nonchilled' & Type == 'Quebec'), 
               x = ~conc, 
               y = ~uptake,
               color = ~Type, 
               text = 'Quebec, nonchilled',
               type = 'scatter',
               mode = 'lines')
fig <- fig %>% add_trace(data = filter(m, Treatment == 'nonchilled' & Type == 'Mississippi'),
                         x = ~conc,
                         y = ~uptake,
                         color = ~Type,
                         text = 'Mississippi, nonchilled',
                         type = 'scatter',
                         mode = 'lines')
fig <- fig %>% add_trace(data = filter(m, Treatment == 'chilled' & Type == 'Quebec'),
                         x = ~conc,
                         y = ~uptake,
                         color = ~Type,
                         text = 'Quebec, chilled',
                         type = 'scatter',
                         mode = 'lines',
                         line = list(dash = 'dash'))
fig <- fig %>% add_trace(data = filter(m, Treatment == 'chilled' & Type == 'Mississippi'),
                         x = ~conc,
                         y = ~uptake,
                         color = ~Type,
                         text = 'Mississippi, chilled',
                         type = 'scatter',
                         mode = 'lines',
                         line = list(dash = 'dash'))
fig <- fig %>% layout(title = 'Carbon Dioxide Uptake in Grass Plants',
                      xaxis = list(title = 'Ambient CO2 (mL/L)'),
                      yaxis = list(title = 'CO2 uptake rate (µmol/m^2 sec)'),
                      showlegend = FALSE)

fig
```

The data indicate that grass plants from Quebec have more cold tolerance than those from Mississippi, reflected by a smaller difference between chilled and unchilled treatments.